SpARC: Sparse Redundant Calibration

### 2016-07-14 paper.tex
starting redundant index function

\section{Complex Optimization}
Scalar direction independent calibration is achieved through solving the following minimization problem:
\begin{equation}
\min_{\bg}\|\br\| = \min_{\bg}\|\bd - \bv(\bg)\|, 
\end{equation}
where
\begin{enumerate}
 \item $\bd$ is the observed visibility vector, i.e. 
 \begin{equation}
  \bd = [d_{pq}] \big \} ~ [pq] = 1\cdots N ~ (p<q).
 \end{equation}
 The vector entry $d_{pq}$ denotes the observed visibility associated with the baseline formed by antenna $p$ and $q$, while $N$ denotes the number or antennas
 in the array. 
 \item $\bg = [g_1,g_2,\cdots,g_N]$ represents the instrumental complex antenna gain vector.
 \item $\bv(\bg)$ denotes the predicted visibility vector, i.e.
 \begin{equation}
  \bv(\bg) = [g_p y_{pq}\conj{g}_q]  \big \} ~ [pq] = 1\cdots N ~ (p<q).
 \end{equation}
 In Eq... $y_{pq}$ denotes the visibility which was created from a skymodel and is associated with antenna $p$ and $q$. [Need to rw this sentence] 
\end{enumerate}

@@

\citet{Smirnov2015} have recently shown that calibration can also be performed using the following complex framework: 
\begin{equation}
\min_{\breve{\bg}}\|\breve{\br}\| = \min_{\breve{\bg}}\|\breve{\bd} - \breve{\bv}(\breve{\bg})\|, 
\end{equation}
where $\breve{\bg} = \big[\bg,\conj{\bg}]^T$, still need to define the other vectors properly....
The above formulation is valid and is in fact equivalent to the real/imaginary formulation from above, since v breve is analytic in its argument and its complex conjugate as a whole if we use the Wirtinger derivative
to define our gradient operator.

@@

>>>>

\section{Complex Optimization}
\subsection{Scalar Calibration}
Scalar direction independent calibration is achieved through solving the following minimization problem:
\begin{equation}
\min_{\bg}\|\br\| = \min_{\bg}\|\bd - \bv(\bg)\|, 
\end{equation}
where
\begin{enumerate}
 \item $\bd$ is the observed visibility vector, i.e. 
 \begin{equation}
  \bd = [d_{pq}] \big \} ~ [pq] = 1\cdots N ~ (p<q).
 \end{equation}
 The vector entry $d_{pq}$ denotes the observed visibility associated with the baseline formed by antenna $p$ and $q$, while $N$ denotes the number or antennas
 in the array. 
 \item $\bg = [g_1,g_2,\cdots,g_N]$ represents the instrumental complex antenna gain vector.
 \item $\bv(\bg)$ denotes the predicted visibility vector, i.e.
 \begin{equation}
  \bv(\bg) = [g_p y_{pq}\conj{g}_q]  \big \} ~ [pq] = 1\cdots N ~ (p<q).
 \end{equation}
 In Eq... $y_{pq}$ denotes the visibility which was created from a skymodel and is associated with antenna $p$ and $q$. [Need to rw this sentence] 
\end{enumerate}

@@

\citet{Smirnov2015} have recently shown that calibration can also be performed using the following complex framework: 
\begin{equation}
\min_{\breve{\bg}}\|\breve{\br}\| = \min_{\breve{\bg}}\|\breve{\bd} - \breve{\bv}(\breve{\bg})\|, 
\end{equation}
where $\breve{\bg} = \big[\bg,\conj{\bg}]^T$, still need to define the other vectors properly....
In the above formulation v breve is analytic in its argument and its complex conjugate as a whole under the assumption that the Wirtinger derivative
is used to define the gradient operator. As v breve is analytic we will are also able to apply the least squares method to .

The Wirtinger derivatives are defined as
\begin{eqnarray}
\frac{\partial}{\partial z} = \frac{1}{2}\left ( \frac{\partial}{\partial x} -  i \frac{\partial}{\partial y} \right ),&~&\frac{\partial}{\partial \conj{z}} = \frac{1}{2}\left ( \frac{\partial}{\partial x} +  i \frac{\partial}{\partial y} \right ) 
\end{eqnarray}
where $z = x + iy$ and $x,y \in \mathbb{R}$. It follows from the above that $\frac{\partial z}{\partial z} = 1,\frac{\partial z}{\partial \conj{z}} = 0,\frac{\partial \conj{z}}{\partial z} = 0$ and $\frac{\partial \conj{z}}{\partial \conj{z}} = 1$.

@@

\subsection{Redundant Calibration}
In eq a sky model is required to generate the predicted visibilities $y_{pq}$ as we have too few equations to also solve for them and the gains. If we use a redundant layout
we can reduce the number of unknowns so that we are able to solve for the sky and the gains simultaneously.

\subsubsection{Antenna indices to redundancy index mapping}
If an array is redundant its redundant baselines sample the exact same visibilites in the $uv$-plane. So even though we label the visibilies belonging to different redundant baselines with
a different composite antenna index they actually represent the same visibilities. Another useful labelling strategy therefore would be to assign redundant indices to each unique
redundant baseline of the array. Where the numbering can start from one and is incrementet every time a new redundant spacing is added to the existing baselines if we 
add one antenna after another to our array in numerical order. A usefull mapping would then be the function that maps composite antenna indices to redundancy indices. 
Let $\phi_{pq}:\mathbb{N}^2\rightarrow\mathbb{N}^+$ be the mapping that maps antenna indices to the redundant spacing indices of the array. Also note that this mapping is not symmetric as 
$\phi_{pq} = 0$ if $p>q$. Moreover, let

\begin{equation}
\psi_{ij} = 
\begin{cases}
q~\textrm{if}~\exists! ~ q \in \mathbb{N} ~ s.t. ~(\phi_{iq} = j)\\
0~\textrm{otherwise}
\end{cases}
\end{equation},

\begin{equation}
\xi_{ij} = 
\begin{cases}
p~\textrm{if}~\exists! ~ p \in \mathbb{N} ~ s.t. ~(\phi_{pi} = j)\\
0~\textrm{otherwise}
\end{cases}
\end{equation}

and

\begin{equation}
\zeta_{ij} = 
\begin{cases}
\phi_{ij}~\textrm{if}~i<j\\
\phi_{ji}~\textrm{if}~i>j\\
0~\textrm{otherwise}
\end{cases}
\end{equation}
